
\thispagestyle{fancy}
	
	\vspace{-2em} % Adjust vertical space as needed
	\begin{center}



\addcontentsline{toc}{subsection}{Editorial Committee}    
\subsection*{\textsc{Editorial Committee}}
	\end{center}
\vspace{1cm}
\onehalfspacing
%\subsubsection*{intenal supervisors}

\begin{longtable}{ L{4.8cm}  L{6.5cm} } 

     Dr. Kasun Nandapala & Director - Admission, Accreditation \& Quality Assurance \\

      Mr. T.D. Denagama & Head, Department of Construction Technology \\

        Ms. W.A.I.M. Gunasekara & Head, Department of Industrial Management \\

       Ms. L.H.D.L. Ranasuriya & Head, Department of Language Studies \\

    Ms. Y. S. Manathunga & Head, Department of Education \& Training \\

     Mr. P.H.S.S. Wijayarathna & Head, Department of Network Technology \\
      
     Dr. (Ms.) J.A.E.C. Jayawardena & Acting Head, Department of Agriculture \& Food Technology \\


   

   

     
    Mr. P Uruthiran & Acting Head, Department of Software Technology \\

   


     Prof. Chandana Jayalath & Professor, Department of  Quantity Surveying \\

     Dr. D.D.D. Suraweera  & Senior Lecturer, Department of Electro-Mechanical Technology\\

     Dr. J.A.D. Jayalath & Senior Lecturer, Multimedia \& Web Technology \\

     Dr. (Ms.) T. Somaratne & Senior Lecturer, Department of Agriculture \& Food Technology \\

       Ms. A.A. Gunawardana & Senior Lecturer, Department of Language Studies \\

         Ms. J.A.M.B. Karunarathna & Senior Lecturer, Department of Language Studies \\

          Ms. W.C.C. Sumathiratna & Senior Lecturer, Department of Building Services Technology \\


           Ms. K.G. Alahapperuma & Senior Lecturer, Department of  Electro-Mechanical Technology \\

             Ms. J.K. Kanthi & Senior Lecturer, Department of  Electro-Mechanical Technology \\

             Ms. M. Thenabadu & Senior Lecturer, Department of Agriculture \& Food Technology \\

         Ms. U. Sivachelvy & Senior Lecturer, Department of Industrial Management \\

             Ms. B.M.T.D. Jayasekara & Senior Lecturer, Department of Industrial Management \\

    

     

   

     

    
             Ms. K .T. P. C. Somarathna & Lecturer (Probationary), Department of Language Studies \\
     
          Ms. A.A.S.U. Gunarathna & Lecturer (Probationary), Department of Construction Technology \\
      

      

      Mr. P.D.S. Ashan & Lecturer (Probationary), Department of Building Services Technology \\

         Mr. H.A. Gayan Madushanka & Lecturer (Probationary), Department of Film \& Television Production Technology \\

    
         Mr. H.N.W. Gunasekara & Lecturer (Probationary), Department of Electro-Mechanical Technology \\

         Mr. A.H.M.S. Siriwardana & Lecturer (Probationary), Department of Construction Technology \\

         Mr. G.A.N. Sampath & Lecturer (Probationary), Department of Film \& Television Production Technology \\

        Mr. S.V.R. Gamage & Lecturer (Probationary), Department of  Electro-Mechanical Technology \\

         

           Mr. L.P.S.S. Dissanayake & Lecturer (Probationary), Department of  software Technology \\

          

       

       

          

         

            
             

          

            

               Dr. S.A.N. Danushka & Teaching Assistant, Department of Education \& Training \\

             Ms. T.R. Vidanapathirane & Teaching Assistant, Department of Industrial Management \\

             

             

            
            
   

    
    
   
    
   
   
   
    
   
    
  
\end{longtable}



\newpage
\singlespacing