
\thispagestyle{fancy}
	
	\vspace{-2em} % Adjust vertical space as needed
	\begin{center}



\addcontentsline{toc}{subsection}{Symposium Organizing Committee}    
    \subsection*{\textsc{Symposium Organizing Committee}}
	\end{center}
\vspace{1cm}
\onehalfspacing
\subsubsection*{Advisory Committee}


\begin{longtable}{ p{4.8cm}  p{6.5cm} } 
  
    Professor C. Mahesh Edirisinghe  & Vice Chancellor   \\
    Dr. D.D.D. Suraweera  & Former Chair – IRS 2017 \\
    Prof. Chandana Jayalath & Former Chair – IRS 2021 \\
    Dr. L.W.S. Kularatne & Former Chair – IRS 2022 \\
    Mr. H.A. Seneviratne & Former Chair – IRS 2023 \\
\end{longtable} 

\subsubsection*{Programme Committee}

\begin{longtable}{ L{4.8cm}  L{6.5cm} } 
    %\rule{0pt}{3ex}
   
    Ms. P.M Perera & Symposium Chair \\
    Ms. Samantha Manawadu & Symposium Co-Secretary \\
    Mr. R.R.M.D.P Rathnayake & Symposium Co-Secretary \\
    % Dr. L.W.S Kularatne & Dean, Faculty of Education \\
    Ms. T.K Malwatte & Dean, Faculty of Information Technology \\
    Dr. Jayalal Wettasinghe & Dean, Faculty of Engineering Technology \\
    Dr. U.A.S. Kamal Edirisinghe & Dean, Faculty of Industrial Technology \\
    Dr. Kasun Nandapala & Director, Admission, Accreditation and Quality Assurance \\
    Mr. S.P.A.R.S. Jayathilaka & Director, Human Resource Development Centre \\
    Mr. A.M.C.K. Gunathilaka & Director, Media \& Information Services \\
    Ms. Dilini Ranasuriya & Head, Department of Language Studies \\
    Ms.Y.S Manathunga & Head, Department of Education \& Training \\
    Ms. Indrachapa Gunasekeara & Head, Department of Management Studies \\
    Ms. S.R.M.P. Seneviratna & Head, Department of Quantity Surveying \\
    Mr. D.T. Ganegoda & Head, Department of Electro Mechanical Technology \\
    Mr. T.D. Denagama & Head, Department of Construction Technology \\
    Dr. (Ms.) J.A.E.C. Jayawardena & Acting Head, Department of Agriculture \& Food Technology \\
    Mr. R.M.C.A.B Rathnayake & Acting Head, Department of Network Technology \\
    Mr. P. Uruthiran & Acting Head, Department of Software Technology \\
    Ms. S.G. Nambuwasam & Acting Head, Department of Multimedia \& Web Technology \\
    Professor R.L.W Koggalage & Associate Professor, Department of Electro Mechanical Technology \\
    Dr. S.D.A Sanjeewa & Senior Lecturer, Department of Electro Mechanical Technology \\
    Dr. Janaka Jayalath & Senior Lecturer, Multimedia \& Web Technology \\
    Dr. (Ms.) T. Somaratne & Senior Lecturer, Department of Agriculture \& Food Technology \\
    
    Dr. S.A.N. Danushka & Teaching Assistant, Department of Education \& Training \\
    Mr. M.G. Dharmasiri & Director General (Covering) / Senior Assistant Registrar (Establishments and Administration) \\
    Mr. R.D.P.I. Priyadarshana & System Administrator \\
    Mr. T.C. Jayamuthuge & Producer \\
\end{longtable}



\newpage
\singlespacing