
\thispagestyle{fancy}
	
	\vspace{-2em} % Adjust vertical space as needed
	\begin{center}



\addcontentsline{toc}{subsection}{List of Reviewers}    
\subsection*{\textsc{List of Reviewers}}
	\end{center}
\vspace{1cm}
\onehalfspacing
%\subsubsection*{intenal supervisors}
\begin{longtable}{ L{4.8cm}  L{6.8cm} }  

    %\rule{0pt}{3ex}
Prof. Ayantha Gomes &  Sri Lanka Institute of Information Technology\\
Prof. W.A.L. Chandrasiri Waliwita &  Gampaha Wickramarachchi University of Indigenous Medicine, Sri Lanka\\
Prof. Chandana Jayalath &  University of Vocational Technology, Sri Lanka\\
Prof. Ravindra Koggalage &  University of Vocational Technology, Sri Lanka\\
Dr. Subodha Muhandiram &  Vorarlberg University of Applied Sciences, Austria\\

Dr. Sanjaya Thilakarathne &  University of Colombo, Sri Lanka\\
Dr. Shashinie M. Thenabadu &  University of Colombo, Sri Lanka\\
Dr. Nayana Amarawickrama &  University of Colombo, Sri Lanka\\
Dr. Buddhika Samarasekara &  University of Sri Jayewardenepura, Sri Lanka\\
Dr. Ravimal Bandara &  University of Sri Jayewardenepura, Sri Lanka\\
Dr. P.B.S.L. Pushpakumara &  University of Sri Jayewardenepura, Sri Lanka\\
Dr. Chathuri Senanayake &  University of Sri Jayewardenepura, Sri Lanka\\
Dr. Mihiri Munasinghe &  University of Sri Jayewardenepura, Sri Lanka\\
Dr. Lochandaka Ranathunga &  University of Moratuwa, Sri Lanka\\
Dr. Nalaka Jayantha &  University of Moratuwa, Sri Lanka\\
Dr. Pasan Henadeera &  University of Moratuwa, Sri Lanka\\
Dr. Prasanna Illankoon &  University of Moratuwa, Sri Lanka\\
Dr. Sumith Gopura &  University of Moratuwa, Sri Lanka\\
Dr. Chamod Hettiarachchi &  University of Moratuwa, Sri Lanka\\
Dr. Kaushalya Wijayasekara &  University of Ruhuna, Sri Lanka\\
Dr. Iromi Ranaweera &  University of Ruhuna, Sri Lanka\\
Dr. Niranjan Kannangara &  University of Ruhuna, Sri Lanka\\
Dr. Chamila Dias &  Open University of Sri Lanka, Sri Lanka\\
Dr. Shakila Pathirana &  University of Kelaniya, Sri Lanka\\
Dr. D. Ashoka Kumara &  General Sir John Kotelawala Defence University, Sri Lanka\\
Dr. Wijendra Gunathilaka &  General Sir John Kotelawala Defence Univesity, Sri Lanka\\
Dr. N.S.D.Madugodage &  Buddhist and Pali University of Sri Lanka\\
Dr. R.M.S.N.Embogama &  University of the Visual and Performing Arts, Sri Lanka\\

Dr. Renuka Perera &  Gampaha Wickramarachchi University of Indigenous Medicine, Sri Lanka\\
Dr. M.W.P. Maduranga &  Sri Lanka Technology Campus\\
Dr. Priyantha Bandara &  Sri Lanka Institute of Information Technology\\
Dr. T.M.A.P.Thennakoon &  Sri Lanka Institute of Advanced Technological Education\\
Dr. K.M.S.K.Karunarathne &  Sri Lanka Institute of Advanced Technological Education\\
Dr. Nialnthi Fernando &  NERD Center, Sri Lanka\\
Dr. Ruvan Abeysekara &  BCAS Campus, Sri Lanka\\
Dr. Dayani Nayantha Kahagala Hewage &  GHD Pty Ltd, Australia\\
Dr. L.W.Sunil Kularatne &  University of Vocational Technology, Sri Lanka\\
Dr. U.A.S.K. Edirisinghe &  University of Vocational Technology, Sri Lanka\\
Dr. D.D.D  Suraweera &  University of Vocational Technology, Sri Lanka\\
Dr. Jayalal Wettasinghe &  University of Vocational Technology, Sri Lanka\\
Dr. M.P.K.C.Nandapala &  University of Vocational Technology, Sri Lanka\\
Dr. Sanjeewa Sondarangallage &  University of Vocational Technology, Sri Lanka\\
Dr. Janaka Jayalath &  University of Vocational Technology, Sri Lanka\\
Dr. S.A.N. Danushka &  University of Vocational Technology, Sri Lanka\\
Dr. J.A.E.C.  Jayawardena &  University of Vocational Technology, Sri Lanka\\
Dr. Thikshani Somarathna &  University of Vocational Technology, Sri Lanka\\
Mr. S.L. Priyantha Fonseka &  University of Peradeniya, Sri Lanka\\
Ms. E.W.Biyiri &  Rajarata University of Sri Lanka\\
Mr. Rasika Jayasinghe &  University of Sri Jayewardenepura, Sri Lanka\\
Ms. Lakmini Kalugampitiya &  University of Sri Jayewardenepura, Sri Lanka\\
Mr. Reshan Perera &  University of Moratuwa, Sri Lanka\\
Ms. Chandi Karunarathna &  Uva Wellassa University, Sri Lanka\\
Ms. W.N. Kawmudi &  General Sir John Kotelawala Defence University, Sri Lanka\\
Mr. Vijayanathan Senthooran &  University of Vavuniya, Sri Lanka\\
Mr. T. Arudchelvam &  Wayamba University of Sri Lanka\\
Mr. Ruchira Abeyweera &  Open University of Sri Lanka\\
Ms. Samindi Perera &  General Sir John Kotelawala Defence University, Sri Lanka\\
Ms. V.K.N. Kurukulaarachchi &  CINEC Campus, Sri Lanka\\
Dr. Harsha Jayakody &  Ministry of Health, Sri Lanka\\
Mr. H.M.Somaratne &  University of Vocational Technology, Sri Lanka\\
Ms. SumaliMorapitiya &  Institute of Technology, University of Moratuwa, Sri Lanka\\
Mr. Mangala Silva &  Synergo Consultancy (Pvt) Ltd, Sri Lanka\\

Mr. Sudheera Mathakadheera &  John Keels Holdings, Sri Lanka\\
Ms. K.G. Alahapperuma &  University of Vocational Technology, Sri Lanka\\
Ms. J.K. Kanthi &  University of Vocational Technology, Sri Lanka\\
Mr. S.P.A.R.S. Jayathilaka &  University of Vocational Technology, Sri Lanka\\
Mr. Dilantha Rathnayake &  University of Vocational Technology, Sri Lanka\\
Mr. D.T. Ganegoda &  University of Vocational Technology, Sri Lanka\\
Mr. P. Uruthiran &  University of Vocational Technology, Sri Lanka\\
Ms. Y.S.Manathunga &  University of Vocational Technology, Sri Lanka\\
Ms. L.H.D.L. Ranasuriya &  University of Vocational Technology, Sri Lanka\\
Ms. R.M.P.Seneviratne &  University of Vocational Technology, Sri Lanka\\
Ms. W.A.I.M.Gunasekara &  University of Vocational Technology, Sri Lanka\\
Mr. H.P.A.I. Pathirana &  University of Vocational Technology, Sri Lanka\\
Ms. P.M  Perera &  University of Vocational Technology, Sri Lanka\\
Ms. Malkanthi Thenabadu &  University of Vocational Technology, Sri Lanka\\
Ms. U. Sivachelvy &  University of Vocational Technology, Sri Lanka\\
Mr. T.D. Denagama &  University of Vocational Technology, Sri Lanka\\
Ms. G.M.S.R.G.Manawadu &  University of Vocational Technology, Sri Lanka\\
Ms. J.A.M.B.Karunarathna &  University of Vocational Technology, Sri Lanka\\
Ms. A.A.Gunawardana &  University of Vocational Technology, Sri Lanka\\
Mr. D. Premarathna &  University of Vocational Technology, Sri Lanka\\
Ms. B.M.T.D. Jayasekara &  University of Vocational Technology, Sri Lanka\\
Ms. K.G.N.P. Rajapaksha &  University of Vocational Technology, Sri Lanka\\
Mr. H.A.G. Madushanka &  University of Vocational Technology, Sri Lanka\\
Mr. H.N.W. Gunasekara &  University of Vocational Technology, Sri Lanka\\
Mr. S.V.R.Gamage &  University of Vocational Technology, Sri Lanka\\
Ms. A.A.S.U. Gunarathne &  University of Vocational Technology, Sri Lanka\\
\end{longtable}    
\newpage
\singlespacing